An automated formal synthesis optimization method for sizing of stand-alone solar photovoltaic systems: case studies and comparative

### 2019-05-30 Tex/elsevier/trindade_appliedenergy_rev0.tex
applied energy text

\begin{abstract}
Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained. Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. %Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments [Nessi].
%Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, 
%unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.
%
%While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS. These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

@@

In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}. 
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.

@@

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented. Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) 
can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%
%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
%
The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely. CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.

@@

A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 

@@

\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}

@@

% -------------------------------------------------------
\subsection{Optimal Sizing of PV Systems}
% -------------------------------------------------------
%%%To select an optimal combination of components from a PV system to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. 
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

@@

Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.

@@

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.
%
% argument is your BibTeX string definitions and bibliography database(s)
\section*{References}
\bibliography{trindadeThesis}{}
%\vspace{12pt}
\end{document}

>>>>

\begin{abstract}
Currently, there exist various methods and tools to size solar photovoltaic systems. The tools are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to obtain optimal sizing of stand-alone PV systems using program synthesis. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first we synthesize the sizing of stand-alone PV systems based in technical issues, but that may not achieve the lowest cost; the optimal solution is then verified iteratively with a lower bound via symbolic model checking, if the verification step do not fail, the lower bound is adjusted and thefails, a counterexample is provided with the optimal sizing, linking the technical response of the first phase with cost analysis of the second phase. is obtainedto the synthesis engine and the process iterates until an optimal sizing is obtained. Commercial equipment data from different manufacturers are provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results using seven case studies show that our synthesis method is able to output within an acceptable run-time the optimal PV system sizing, and a comparative with a specialized simulation tool shows the effectiveness of our approach.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Cyber-Physical Systems  (CPS) are engineered systems, which are built from, and depend upon, 
the seamless integration of computational  and  physical  components~\cite{NSF2015}. 
During operation, such components must frequently adapt to the executing environment changes 
faced at run-time (dynamics of the physical processes) and must be able to continue to behave 
in a controlled and safe way, thus posing novel technical challenges for the software engineering of services and applications for CPS~\cite{Metzger2014}. Important quality aspects for CPS include scalability, e.g., ensuring that CPS applications can scale to urban-wide deployment environments~\cite{NESSI}.
Software pervasiveness in CPS places new challenges; in particular, highly dynamic environments, rapidly changing requirements, unpredictable and uncertain operating conditions demand new paradigms for software design~\cite{Filieri2015}.

While some research efforts do exist to enhance and optimize the software development processes for CPS, further investigation and discussion of better and more effective models are still needed in practice~\cite{Al-Jaroodi2016}. 
Among the opportunities for enhancements in the software development processes for CPS, there exists the need for developing new techniques and tools to support CPS requirements gathering and analysis with the goal of synthesizing correct-by-construction implementations of CPS. These techniques need to deal with predefined requirements enforced by the nature and inherited constraints of the target CPS. In addition, they should be able to provide verification and validation mechanisms for completeness, correctness, and consistency~\cite{Al-Jaroodi2016}. Uncertainty and variability, at the same time, can be dealt with formal verification~\cite{NESSI}. Energy production, distribution, and optimization are all CPS problems~\cite{UC}.

@@

In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen, HOMER, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.  However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}. 
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.

@@

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in synthesizing PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) 
can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.

\textit{Outline}. Section~\ref{sec:Background} gives the background about related works, program synthesis, design sizing and validation of PV systems, and the mathematical modeling. Section~\ref{sec:Method} presents the automated formal synthesis proposed by this work. Section~\ref{sec:Results} is devoted to the experimentation, results and discussions. Section~\ref{sec:Conclusion} presents the conclusion and describes future work.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:Background}
%-----------------------------------------------------------
%
\subsection{State-of-art in Automated Verification of Electrical Systems}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The conversion of traditional power grid into a smart grid, a fundamental example of a CPS, raises a number of issues that requires novel methods and applications. In 2012, a Chinese smart grid implementation was considered as case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}. The authors employed a stochastic model checking approach and presented a modelling and analysis study using PRISM~\cite{KwiatkowskaNP11}. The focus of this study was on how CPS integrate information and communication technology functions to the physical elements of a system for monitoring and controlling purposes; here the authors employed automated verification of certain quantitative properties of the system, as 	probability	of	node	failure	in	the	long run, impact	of	repair	service	on	the	failure	risk, and expected energy consumption, with no interest in power generation or even solar PV systems.

In 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}. The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework. The initial focus was on relay operations and test-case generation to ensure early detection of design errors. The study was limited to power system protection and did not deal with electricity generation or even solar PV systems.

Other related studies from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking for CPS in terms of non-functional properties such as time and energy~\cite{Cheng2015}. In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios. The focus here is on smart buildings and HVAC (heating, ventilation, and air conditioning) systems. The research did no deal with solar PV systems.

In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}. The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness. The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''. The author used approximate model checking of stochastic and hybrid models.

In 2018, a verification methodology was proposed for the Cyber Physical Energy Systems (CPES) with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}. This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios. The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior. The work did not include the other components of a stand-alone solar PV system.

Another work from 2018 was the approach to modeling smart grid components using a formal specification. The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}. The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods. The starting point of this study was that a smart home can be considered as an integrated system consisting of various objects and system, which communicates and interacts with each other. This approach is base on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
%
The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that partially satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely. CEGIS represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur}.

@@

A PV system is illustrated in Fig.\ref{fig:blockdiagram}. It identifies the PV generator, batteries, charge controller, inverter, and AC load. 

@@

\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}

@@

% -------------------------------------------------------
\subsection{Optimal Sizing of PV Systems}
% -------------------------------------------------------
%
%%%To select an optimal combination of components from a PV system to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
The optimal sizing of PV systems is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the acquisition cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{METHOD}
\label{sec:Method}

\subsection{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking. 
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE Initialize variables \\
  \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
%  \STATE Declare list of controllers data and cost \\
%  \STATE Declare list of batteries data and cost \\
%  \STATE Declare list of inverters data and cost \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Declare power demand, power peak, energy consumption \\
  \STATE Declare battery autonomy, deep of discharge, AC voltage \\
  \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC )$ \\
%	\STATE Requirement enforced by \textbf{assume}$(V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
%	\STATE Requirement enforced by \textbf{assume}$(P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}
%

@@

Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.

\subsection{Assumptions and Premises}

%---------------------------------------------------------------------------
\section{RESULTS AND DISCUSSION}
\label{sec:Results}
%---------------------------------------------------------------------------
\textbf{Case studies.} We have performed two stand-alone PV system case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.

@@

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: using Net Present Cost (NPC), or Levelized Cost of Energy (LCOE) criteria, in order to promote the acceptability of investment, or to include operational and maintenance costs to the adopted Life Cycle Cost (LCC) analysis performed at this paper; (3) to increase the equipment and manufacturers data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained and it allows a simulation-verification comparative.

\section{CONCLUSIONS}
Conclusions here
\label{sec:Conclusion}
%
% argument is your BibTeX string definitions and bibliography database(s)
%\section*{REFERENCES}
\bibliography{trindadeThesis}{}
%\vspace{12pt}
\end{document}
